---
title: "EDA initial dataset"
author: "Juan Sebastian Aristizabal Ortiz"
date: "7 12 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=TRUE, eval = TRUE}
library(dplyr)
library(here)
library(stringr)
library(data.table)
# library(scoringutils)
# library(purrr)
# library(tidyr)
library(ggplot2)
```

## Setting:
Quantile based data: forecasts provide a predictive distribution. 
   * 23 quantiles = 11 prediction intervals + median prediction. 

> Specifying how likely the true observed value will fall in a given range. 


## Main questions to be solved by this EDA: 
   - Show me the quantiles
   - Show me the median prediction
   - Does every quantile has an assigned corresponding probability?

## EDA

Load the data set. Next chunk can't be evaluated because RStudion doesn't find the path.
I load the `hub_data` from the dataset.Rmd file in the data folder. 

```{r, eval = FALSE}
hub_data <- rbindlist(
  list(
    fread("full-data-european-forecast-hub-1.csv"), 
    fread("full-data-european-forecast-hub-2.csv")
  )
)
```








